---
title: "520-Project 3 Bayesian Inference for Hunitng"
author: "Janish Parikh"
date: "10/16/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r cars}
library(ggplot2)
library(reshape)
```

# Load Data
```{r}
data <- read.csv("~/Desktop/520-Intro to AI/Project3/Repeated_Forward_Astar/cmp_data_5.csv", header=FALSE)
colnames(data)<-c("Sample","dim","agent","terrain","move","exam","total")
head(data)
```

# Defining Theme for better Plots
```{r}
mynamestheme <- theme(plot.title = element_text(family = "Courier", face = "bold", size = (12)), 
legend.title = element_text(colour = "Black",  face = "bold.italic", family = "Helvetica"), 
legend.text = element_text(face = "italic", colour="steelblue4",family = "Helvetica"), 
axis.title = element_text(family = "Helvetica",face = "bold.italic", size = (10), colour = "Black"),
axis.text = element_text(family = "Courier", colour = "cornflowerblue", size = (10)))
```

# Plot of Total Action Cost V/S Dimension of Gridworld
```{r}
test1 <- data[,c("agent","dim","total")]
v1<-aggregate(test1[test1$agent==6,]$total,list(test1[test1$agent==6,]$dim), mean)
v2<-aggregate(test1[test1$agent==7,]$total,list(test1[test1$agent==7,]$dim), mean)
v3<-aggregate(test1[test1$agent==8,]$total,list(test1[test1$agent==8,]$dim), mean)

colnames(v1)<-c("Gridworld_Dimension","Agent 6")
colnames(v2)<-c("Gridworld_Dimension","Agent 7")
colnames(v3)<-c("Gridworld_Dimension","Agent 8")

MergedDF <- merge(v1, v2, by="Gridworld_Dimension")
MergedDF <- merge(MergedDF, v3, by="Gridworld_Dimension")

Molten <- melt(MergedDF, id.vars = "Gridworld_Dimension")
gp1 <- ggplot(Molten, aes(x = Gridworld_Dimension, y = value, colour = variable)) +
 geom_point()+ 
 geom_line(aes(y = value, x =Gridworld_Dimension ))+
 scale_color_discrete("Agent Type")+
 theme_minimal()+
 theme(legend.position="top")

print(gp1 + mynamestheme + labs( y="Average Total Cost (Movement + Examination)", x = "Gridworld Dimension"))
```

# Plot for Average Movement Cost V/S Dimension of Gridworld
```{r}
test1 <- data[,c("agent","dim","move")]
v1<-aggregate(test1[test1$agent==6,]$move,list(test1[test1$agent==6,]$dim), mean)
v2<-aggregate(test1[test1$agent==7,]$move,list(test1[test1$agent==7,]$dim), mean)
v3<-aggregate(test1[test1$agent==8,]$move,list(test1[test1$agent==8,]$dim), mean)

colnames(v1)<-c("Gridworld_Dimension","Agent 6")
colnames(v2)<-c("Gridworld_Dimension","Agent 7")
colnames(v3)<-c("Gridworld_Dimension","Agent 8")

MergedDF <- merge(v1, v2, by="Gridworld_Dimension")
MergedDF <- merge(MergedDF, v3, by="Gridworld_Dimension")

Molten <- melt(MergedDF, id.vars = "Gridworld_Dimension")
gp1 <- ggplot(Molten, aes(x = Gridworld_Dimension, y = value, colour = variable)) +
 geom_point()+ 
 geom_line(aes(y = value, x =Gridworld_Dimension ))+
 scale_color_discrete("Agent Type")+
 theme_minimal()+
 theme(legend.position="top")

print(gp1 + mynamestheme + labs( y="Average Movement Cost", x = "Gridworld Dimension"))
```

# Plot for Average Examination Cost V/S Dimension of Gridworld
```{r}
test1 <- data[,c("agent","dim","exam")]
v1<-aggregate(test1[test1$agent==6,]$exam,list(test1[test1$agent==6,]$dim), mean)
v2<-aggregate(test1[test1$agent==7,]$exam,list(test1[test1$agent==7,]$dim), mean)
v3<-aggregate(test1[test1$agent==8,]$exam,list(test1[test1$agent==8,]$dim), mean)

colnames(v1)<-c("Gridworld_Dimension","Agent 6")
colnames(v2)<-c("Gridworld_Dimension","Agent 7")
colnames(v3)<-c("Gridworld_Dimension","Agent 8")

MergedDF <- merge(v1, v2, by="Gridworld_Dimension")
MergedDF <- merge(MergedDF, v3, by="Gridworld_Dimension")

Molten <- melt(MergedDF, id.vars = "Gridworld_Dimension")
gp1 <- ggplot(Molten, aes(x = Gridworld_Dimension, y = value, colour = variable)) +
 geom_point()+ 
 geom_line(aes(y = value, x =Gridworld_Dimension ))+
 scale_color_discrete("Agent Type")+
 theme_minimal()+
 theme(legend.position="top")

print(gp1 + mynamestheme + labs( y="Average Examination Cost", x = "Gridworld Dimension"))
```

# Looking where target hidden in Flat Terrain Type. 
```{r}
test1 <- data[data$terrain==2,c("agent","dim","total")]
v1<-aggregate(test1[test1$agent==6,]$total,list(test1[test1$agent==6,]$dim), mean)
v2<-aggregate(test1[test1$agent==7,]$total,list(test1[test1$agent==7,]$dim), mean)
v3<-aggregate(test1[test1$agent==8,]$total,list(test1[test1$agent==8,]$dim), mean)

colnames(v1)<-c("Gridworld_Dimension","Agent 6")
colnames(v2)<-c("Gridworld_Dimension","Agent 7")
colnames(v3)<-c("Gridworld_Dimension","Agent 8")

MergedDF <- merge(v1, v2, by="Gridworld_Dimension")
MergedDF <- merge(MergedDF, v3, by="Gridworld_Dimension")

Molten <- melt(MergedDF, id.vars = "Gridworld_Dimension")
gp1 <- ggplot(Molten, aes(x = Gridworld_Dimension, y = value, colour = variable)) +
 geom_point()+ 
 geom_line(aes(y = value, x =Gridworld_Dimension ))+
 scale_color_discrete("Agent Type")+
 theme_minimal()+
 theme(legend.position="top")

print(gp1 + mynamestheme + labs( y="Average Total Cost (Movement + Examination)", x = "Gridworld Dimension"))
```

# Looking where target hidden in Hilly Terrain Type. 
```{r}
test1 <- data[data$terrain==5,c("agent","dim","total")]
v1<-aggregate(test1[test1$agent==6,]$total,list(test1[test1$agent==6,]$dim), mean)
v2<-aggregate(test1[test1$agent==7,]$total,list(test1[test1$agent==7,]$dim), mean)
v3<-aggregate(test1[test1$agent==8,]$total,list(test1[test1$agent==8,]$dim), mean)

colnames(v1)<-c("Gridworld_Dimension","Agent 6")
colnames(v2)<-c("Gridworld_Dimension","Agent 7")
colnames(v3)<-c("Gridworld_Dimension","Agent 8")

MergedDF <- merge(v1, v2, by="Gridworld_Dimension")
MergedDF <- merge(MergedDF, v3, by="Gridworld_Dimension")

Molten <- melt(MergedDF, id.vars = "Gridworld_Dimension")
gp1 <- ggplot(Molten, aes(x = Gridworld_Dimension, y = value, colour = variable)) +
 geom_point()+ 
 geom_line(aes(y = value, x =Gridworld_Dimension ))+
 scale_color_discrete("Agent Type")+
 theme_minimal()+
 theme(legend.position="top")

print(gp1 + mynamestheme + labs( y="Average Total Cost (Movement + Examination)", x = "Gridworld Dimension"))
```

# Looking where target hidden in Forest Terrain Type. 
```{r}
test1 <- data[data$terrain==8,c("agent","dim","total")]
v1<-aggregate(test1[test1$agent==6,]$total,list(test1[test1$agent==6,]$dim), mean)
v2<-aggregate(test1[test1$agent==7,]$total,list(test1[test1$agent==7,]$dim), mean)
v3<-aggregate(test1[test1$agent==8,]$total,list(test1[test1$agent==8,]$dim), mean)

colnames(v1)<-c("Gridworld_Dimension","Agent 6")
colnames(v2)<-c("Gridworld_Dimension","Agent 7")
colnames(v3)<-c("Gridworld_Dimension","Agent 8")

MergedDF <- merge(v1, v2, by="Gridworld_Dimension")
MergedDF <- merge(MergedDF, v3, by="Gridworld_Dimension")

Molten <- melt(MergedDF, id.vars = "Gridworld_Dimension")
gp1 <- ggplot(Molten, aes(x = Gridworld_Dimension, y = value, colour = variable)) +
 geom_point()+ 
 geom_line(aes(y = value, x =Gridworld_Dimension ))+
 scale_color_discrete("Agent Type")+
 theme_minimal()+
 theme(legend.position="top")

print(gp1 + mynamestheme + labs( y="Average Total Cost (Movement + Examination)", x = "Gridworld Dimension"))
```
